GMSE: a general tool for management strategy evaluation

### 2017-09-15 notebook/presentation/GMSE_presentation.Rmd
Update slides, mostly to the introduction

![](mannahatta_before.jpg)

@@

![](mannahatta.jpg)

@@

@@

## Uncertainty in natural resource management

Uncertainty is fundamental in ecological and economic systems, and their measurement

**Natural resources**: Structural and demographic uncertainty

**Resource observation**: Observation uncertainty

**Management**: Implementation uncertainty

**Stake-holder actions**: Pay-off uncertainty

@@

[Adami et al. (2016) Phys. Life. Rev. 19:1-26](http://dx.doi.org/10.1016/j.plrev.2016.08.015)

>>>>

![](mannahatta_before.png)

@@

![](mannahatta.png)

@@

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Computer Image: [Markley Boyer](https://www.facebook.com/markley.boyer), Photo Image: [Robert Clark](http://www.nationalgeographic.com/contributors/c/photographer-robert-clark/)  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [National Geographic](http://ngm.nationalgeographic.com/2009/09/manhattan/miller-text), [The Welikia Project](https://welikia.org/)

![](potato_fields_Janet_Tench.jpg)

Image: [Janet Tench](https://commons.wikimedia.org/wiki/File:Norfolk_potato_field_-_geograph.org.uk_-_180521.jpg)
</center>

![](KehoeFig1.png)

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [Kehoe et al. (2017) *Nat. Ecol. Evol.* **1**:1129–1135](https://www.nature.com/articles/s41559-017-0234-3)

@@

![](mse_overview_sm_pt.png)

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [Bunnefeld et al. (2011) *Trends. Ecol. Evol.* **26**:441-447](https://doi.org/10.1016/j.tree.2011.05.003)  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [Chadès et al. (2017) *Theor. Ecol.* **10**:1-10](https://doi.org/10.1007/s12080-016-0313-0)

![](mse_overview_sm_un.png)

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [Bunnefeld et al. (2011) *Trends. Ecol. Evol.* **26**:441-447](https://doi.org/10.1016/j.tree.2011.05.003)  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [Chadès et al. (2017) *Theor. Ecol.* **10**:1-10](https://doi.org/10.1007/s12080-016-0313-0)

@@

[Adami et al. (2016) *Phys. Life. Rev.* **19**:1-26](http://dx.doi.org/10.1016/j.plrev.2016.08.015)
